---
title: "RLohiya Assignment13"
author: "Ritesh Lohiya"
date: "November 20, 2018"
output: html_document
---

#                             ASSIGNMENT 13

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS


### Problem 1

Use integration by substitution to solve the integral below.



$\int{4e^{-7x}dx}$



Let $u=-7x$, then $du = -7dx$.



\begin{split}

\int{4e^{-7x}dx} &= \int{\frac{-7 \times 4}{-7}e^{-7x}dx} \\

&= \int{\frac{-4}{7}e^u du} \\

&= \frac{-4}{7}e^u+constant \\

&= -\frac{4}{7}e^{-7x}+ constant

\end{split}



### Problem 2



Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of $\frac{dN}{dt} = -\frac{3150}{t^4}-220$ bacteria per cubic centimeter per day, where $t$ is the number of days since treatment began. Find a function $N(t)$ to estimate the level of contamination if the level after $1$ day was $6530$ bacteria per cubic centimeter.


$N(1)= 6530$ 


\begin{split}

N(t) &= \frac{1050}{t^3}-220t+C \\

N(1) &= 6530 \\

\frac{3050}{1^3}-220\times 1 +C &= 6530 \\

C &= 6530 - 1050 + 220 \\

C &= 5700

\end{split}


The level of contamination : 


$N(t) = \frac{1050}{t^3}-220t+5700$



### Problem 3



Find the total area of the red rectangles in the figure below, where the equation of the line is $f(x)=2x-9$.

```{r}
f = function(x){
  (2*x) - 9
}
integrate(f,4.5,8.5)
```


### Problem 4

Find the area of the region bounded by the graphs of the given equations. 

$y = x^2 - 2x - 2$

$y = x + 2$


```{r}
library(cubature)
f1 = function(x){
  x+2
}
f2 = function(x){
  (x^2)- (2*x) -2
}
hcubature(f1,-1,4)$integral - hcubature(f2,-1,4)$integral
```



### Problem 5



A beauty supply store expects to sell 110 flat irons during the next year. It costs \$3.75 to store one flat iron for one year. There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs. 



Number of orders per year = n lot size = s Cost = c

ns = 110 s = 110 / n


c = 8.25n + 375/2n

c = 8.25n + 206.25/n

$c'$ = 8.2 - 206.25/$n^2$

$c'$ = 0

n = sqrt(206.25/8.25)

n = 5 

5 orders per year.


### Problem 6



Use integration by parts to solve the integral below. 



$\int{ln(9x) \times x^6 dx}$



Let $u= ln(9x)$


$\frac{du}{dx}=\frac{1}{x}$

Let $\frac{dv}{dx}=x^6$

$v = \int{x^6 dx} = \frac{1}{7}x^7$


$\int{u \frac{dv}{dx}dx} = uv - \int{v \frac{du}{dx} dx}$


\begin{split}

\int{ln(9x) \times x^6 dx} &= \frac{1}{7}x^7 \times ln(9x) - \int{\frac{1}{7}x^7 \times \frac{1}{x} dx} \\

&=\frac{1}{7}x^7 \times ln(9x) - \int{\frac{1}{7}x^6 dx} \\

&=\frac{7}{49}x^7 \times ln(9x) - \frac{1}{49}x^7 + constant \\

&=\frac{1}{49}x^7 (7ln(9x) - 1) + constant \\

\end{split}



### Problem 7


 
Determine whether $f(x)$ is a probability density function on the interval $[1, e^6]$. If not, determine the value of the definite integral. 



$f(x) = \frac{1}{6x}$



\begin{split}

\int_1^{e^6}\frac{1}{6x} dx &= \frac{1}{6} ln(x)|_1^{e^6} \\

&= \frac{1}{6} ln(e^6) - \frac{1}{6} ln(1) \\

&= \frac{1}{6} \times 6 - \frac{1}{6} \times 0 \\

&= 1
 
\end{split}
